---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
df<- read.csv("~/Downloads/Fitness Club Data .csv")
```

```{r}
sum(is.na(df))
```


```{r}
library(dplyr) 
library(stringr) 
library(caTools) 

```




Calculate basic stats descriptive statistics (mean, median, min, max, standard deviation) for each field 

```{r}
summary(df)
```









Visualize distributions of data elements using histograms for key variables and predict which variables you expect to be most correlated with default/churn. 

```{r}
hist(df$price)
```


```{r}
hist(df$downpmt)
```


```{r}
plot(as.factor(df$use))
```


```{r}
plot(as.factor(df$gender))
```


```{r}
plot(as.factor(df$age))
```
```{r}
hist(df$default)
```

```{r}
plot(as.factor(df$pmttype))
```


```{r}
hist(df$monthdue)
```

```{r}
hist(df$price)
```


Build a Logistic Regression Model to Predict Churn/Retention, you may choose to identify groups within the data to narrow your focus on. (The "default" variable = churn, you may choose to only use age and payment type to build a model to predict "default" = churn) 

```{r}
#test train split
set.seed(42) 
sampleSplit <- sample.split(Y=df$default, SplitRatio=0.8) 
trainSet <- subset(x=df, sampleSplit==TRUE) 
testSet <- subset(x=df, sampleSplit==FALSE)
```

```{r}
model <- glm(as.factor(default) ~pmttype+use+downpmt+as.factor(gender)+price+monthdue, family=binomial(link='logit'), data=trainSet)
```

Display the output visually using charts of your choosing and explain your choice. (ROC Curve, Confusion Matrix, Gains Table) 
```{r}
summary(model)
```


```{r}
probabs <- predict(model, testSet, type='response') 
preds <- ifelse(probabs > 0.5, 1, 0)
```

```{r}
library(caret)
```



```{r}
confusionMatrix(as.factor(preds), as.factor(testSet$default))
```

```{r}
library(pROC)
roc <- roc(testSet$default,probabs) #creates an object with all sorts of diagnostics including sensitivities and specificities

testSet$sens <- roc$sensitivities[2:4970] #include sensitivities in test data
testSet$spec <- roc$specificities[2:4970]

ggplot(testSet, aes(x=spec, y=sens)) + geom_line()
```


```{r}
library(ROCit)
## Warning: package 'ROCit' was built under R version 3.5.2
ROCit_obj <- rocit(score=preds,class=testSet$default)
plot(ROCit_obj)
```





```{r}
library(PRROC)

PRROC_obj <- roc.curve(scores.class0 = preds, weights.class0=testSet$default,
                       curve=TRUE)
plot(PRROC_obj)
```



```{r}
preds_new <- ifelse(probabs > 0.3, 1, 0)
```



```{r}
library(PRROC)

PRROC_obj <- roc.curve(scores.class0 = preds_new, weights.class0=testSet$default,
                       curve=TRUE)
plot(PRROC_obj)
```



```{r}
confusionMatrix(as.factor(preds_new), as.factor(testSet$default))
```

```{r}
varImp(model, scale = FALSE)
```

