---
title: "MSCA31006_HW2_Zihao_Liu"
output:
  pdf_document: default
  html_document: default
  word_document: default
date: '2022-04-05'
---

```{r}
library(fpp)
library(fpp3)
library(tseries)

library(ggplot2)

library(forecast)
library(dplyr)
```

Question 1

```{r}
load("~/Downloads/visitors.rda")
```

```{r}
visitors_new=select(visitors,-c(Quarter,Origin))
visitorstimeseries=ts(visitors_new,frequency = 4,start = c(1981,1))
```


```{r}

plot(visitorstimeseries)
```

```{r}
Acf(visitorstimeseries)
```

Answer:1980 Q1 to 2012 Q3, there is a up rising trend with seasonal patterns. It seems that there is an increasing shock between 1985 and 1990,2000 and 2002. The data seems to be non-stationary.

Question2

```{r}
fit_add <- decompose(visitorstimeseries, type="additive")

plot(fit_add)
```

```{r}
fit_mult <- decompose(visitorstimeseries, type="multiplicative")

plot(fit_mult)
```


Answer: The appropriate Holt-Winters method for this data set is multiplicative as the time plot shows that the seasonal variation in the data increases as the level of the series increases.

Question3

```{r}
#Linear trend with additive seasonality
m_1=hw(visitorstimeseries,seasonal = "additive",h=16)
#Linear trend with multiplicative seasonality
m_2=hw(visitorstimeseries,seasonal = "multiplicative",h=16)
#Linear trend with additive seasonality and damping
m_3=hw(visitorstimeseries,seasonal = "additive",h=16,damped = TRUE)
#Linear trend with multiplicative seasonality and damping
m_4=hw(visitorstimeseries,seasonal="multiplicative",h=16,damped = TRUE)
```

```{r}
#using Seasonal naïve method
m_5=snaive(visitorstimeseries, h = 16)
```

Question4

```{r}
accuracy(m_1)
accuracy(m_2)
accuracy(m_3)
accuracy(m_4)
accuracy(m_5)
```

Answer:
We find that the model Linear trend with multiplicative seasonality and damping has the lowest RMSE.Its RMSE is 7460.002 As a result, I prefer the forth model.

Question5

```{r}
 checkresiduals(m_4)
```
```{r}
summary(m_4)
```

Answer:  
The residuals are centered around 0 but the residuals may not be normal as the histogram has a long right tail. The Acf shows most lags are within confidence intervals.In Ljung-Box test, The p-value is close to zero so we rejected the null hypothesis that the residuals are independently distributed. Residuals are not white noise.
Smoothing parameters: alpha = 0.52 beta = 0.0027 gamma = 1e-04 phi = 0.98
